---
title: "IMDB Data Preprocessing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
```

## Part I: Preprocessing

* [Edit your `.gitignore` file](https://docs.github.com/en/get-started/getting-started-with-git/ignoring-files) to ignore all files with the `.rda` extension. (Add and commit)

* Create a new file in the `data/` directory called "Preprocessing.Rmd". The remaining instructions in this section are to be completed in that file.

* Write a function that will load a table from the IMDb files in the `data/` directory.
  * The function should take the file name (without the ".csv.gz" portion) as an argument
  * The function should load the appropriate `.csv.gz` file.
  * Make sure that all "\\N" values (which IMDB uses to indicate missing values) are turned into proper NA values in R
  * The function should return the table.

```{r preprocess-function}
preprocess <- function(file_name) {
  file_path <- file.path("data", paste0(file_name, ".csv.gz"))
  table <- readr::read_csv(file_path, na = "\\N")
  return(table)
}
```


* For each of the `.csv.gz` files, use your function to load the table, then save it into a variable (e.g. `name_basics <- preprocess("name_basics")`) and use the `write_rds` function (e.g., `write_rds(name_basics, "name_basics.rda")`.

```{r}
name_basics <- preprocess("name_basics_sample")
write_rds(name_basics, "data/name_basics_sample.rda")

title_basics <- preprocess("title_basics_sample")
write_rds(title_basics, "data/title_basics_sample.rda")

title_ratings <- preprocess("title_ratings_sample")
write_rds(title_ratings, "data/title_ratings_sample.rda")

title_principals <- preprocess("title_principals_sample")
write_rds(title_principals, "data/title_principals_sample.rda")
```

* Run the function on all of the `*_sample.csv.gz` files to created processed `.rda` files.
* In your other files, you can load these using the `TABLE <- read_rds("data/FILENAME.rda")` function.

```{r}
name_basics <- read_rds("data/name_basics_sample.rda")
title_basics <- read_rds("data/title_basics_sample.rda")
title_ratings <- read_rds("data/title_ratings_sample.rda")
title_principals <- read_rds("data/title_principals_sample.rda")
```

